---
title: "Cite original publications"
author: "Beni Stocker"
date: "2024-07-1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy = FALSE )
```

Read and subset citation data.

```{r}
library(tidyverse)
library(here)
library(xtable)

source(here("R/create_table_latex.R"))

source(here("R/process_cite_lines.R"))

#take a sample of citations from the mesi_db bibliography. The list should contain the experiments and citations used in your analysis.
# 
df <- read_csv(here("data/mesi_bibliography.csv"),show_col_types = FALSE) |> 
  slice(1:10) |> 
  select(exp, citation) |> 
  arrange(citation) |>
  mutate(citation = paste0('\\', "cite{", citation, "}"))


```  


The data frame created above can now be written as a Latex table as Latex source code that can be placed in a Latex document.

```{r}
#create latex file containing just the table in latex source code -> table.tex
create_table_latex(df, caption = "This is an example of a Caption text", filn = here("latex/table.tex") )
```

```{r}
# Modify the .tex file in order to be compatible with latex. eventually you will need to correct other special symbols manually in the output.tex file before including it into your document.

# Read the .tex file
lines <- readLines(here("latex/table.tex"))

# Apply the processing function to each line
modified_lines <- process_cite_lines(lines)

# Write the modified lines to a new .tex file
writeLines(modified_lines, here("latex/output.tex"))
```

This creates an output.tex file looking like this: 
```
% latex table generated in R 4.4.0 by xtable 1.8-4 package
% Mon Jul  1 14:35:22 2024
\begin{table}[ht]
\centering
\begin{tabular}{ll}
  \hline
exp & citation \\ 
  \hline
helsinki\_d & \cite{aaltonen_et_al_2016}   \\
  62.88\_27.67\_f & \cite{aarnio_and_martikainen_1995}   \\
  riceface\_shizukuishi\_l\_2007\_c & \cite{adachi_et_al_2014}   \\
  riceface\_shizukuishi\_l\_2007\_cw & \cite{adachi_et_al_2014}   \\
  riceface\_shizukuishi\_l\_2007\_w & \cite{adachi_et_al_2014}   \\
  riceface\_shizukuishi\_l\_2008\_c & \cite{adachi_et_al_2014}   \\
  riceface\_shizukuishi\_l\_2008\_cw & \cite{adachi_et_al_2014}   \\
  riceface\_shizukuishi\_l\_2008\_w & \cite{adachi_et_al_2014}   \\
  biocon\_cfs & \cite{adair_et_al_2009}   \\
  biocon\_cs & \cite{adair_et_al_2009}   \\
  \end{tabular}
\caption{This is an example of a Caption text} 
\end{table}

```



#### further instructions

Next, place the table source into a Latex source file by `\include{output.tex}`. As an example, see file `latex/example.tex`. Compile that file for example from the terminal with `pdflatex example.tex` and `bibtex example`. Make sure that you change into the subdirectory `latex/` before executing the compilation commands. Then open the file `example.pdf`.
